\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: POC\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member up to the POC
Demo.  The time period of interest is the time between the beginning of the term
and the POC demo.

\section{Demo Plans}

Our team will be demonstrating a simple POC for our project. This will involve accepting a user submission of matlab code through a webpage, executing the code on the backend, and displaying the reuslt of the execution to the user on the webpage.

\section{Team Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 9\\
Declan Young & 9\\
Aidan Mariglia & 9\\
Nathan Uy & 9\\
Ben Dubois & 9\\
\bottomrule
\end{tabular}
\end{table}

\section{Supervisor/Stakeholder Meeting Attendance}


\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 5\\
Declan Young & 5\\
Aidan Mariglia & 5\\
Nathan Uy & 5\\
Ben Dubois & 5\\
\bottomrule
\end{tabular}
\end{table}


\section{Lecture Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 5\\
Declan Young & 5\\
Aidan Mariglia & 5\\
Nathan Uy & 5\\
Ben Dubois & 5\\
\bottomrule
\end{tabular}
\end{table}

We only included lectures 7 onward as only those have GitHub issues, but everyone attended the previous lectures as well.

\section{TA Document Discussion Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 3\\
Declan Young & 3\\
Aidan Mariglia & 3\\
Nathan Uy & 2\\
Ben Dubois & 3\\
\bottomrule
\end{tabular}
\end{table}

Nathan missed one TA meeting due to a scheduling conflict.

\section{Commits}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 15 & 100\% \\
Declan Young & 6 & 37.5\% \\
Aidan Mariglia & 6 & 37.5\% \\
Nathan Uy & 2 & 18.75\% \\
Ben Dubois & 1 & 6.25\% \\
\bottomrule
\end{tabular}
\end{table}

All (3) major commits are coauthored by all team members.

\section{Issue Tracker}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Declan Young & 1 & 0 \\
Aidan Mariglia & 1 & 0 \\
Nathan Uy & 5 & 0 \\
Ben Dubois & 2 & 0 \\
\bottomrule
\end{tabular}
\end{table}

We have not yet officially assigned issues to individual persons. We will pick up tasks depending on availability.

\section{CICD}

CI/CD will be used to enforce branch protection and maintain code quality, running static checks against the code base as well as requiring all existing unit tests to pass before a feature branch can be merged to the main branch.

\end{document}