\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: Rev 0\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member for the Rev 0
Demo.  The time period of interest is the time between the POC demo and the Rev
0 demo.

\section{Demo Plans}

For revision 0, we plan on demonstrating a nearly fully functioning application with an updated user interface based on the design documents we've completed. However, due to the full model taking several hours to run, we'll only be running a shortened version of the model for the demonstration. The demonstration will be conducted using local development only, and hosting will not be set up yet.

\section{Team Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 9\\
Declan Young & 9\\
Aidan Mariglia & 9\\
Nathan Uy & 9\\
Ben Dubois & 9\\
\bottomrule
\end{tabular}
\end{table}


\section{Supervisor/Stakeholder Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 3\\
Declan Young & 3\\
Aidan Mariglia & 3\\
Nathan Uy & 3\\
Ben Dubois & 3\\
\bottomrule
\end{tabular}
\end{table}

\section{Lecture Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 2\\
Declan Young & 2\\
Aidan Mariglia & 2\\
Nathan Uy & 2\\
Ben Dubois & 2\\
\bottomrule
\end{tabular}
\end{table}

We only included lectures 7 onward as only those have GitHub issues, but everyone attended the previous lectures as well.

\section{TA Document Discussion Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 1\\
Declan Young & 0\\
Aidan Mariglia & 0\\
Nathan Uy & 1\\
Ben Dubois & 1\\
\bottomrule
\end{tabular}
\end{table}

Declan and Aidan missed one TA meeting because they were on the McMaster Ski Club trip

\section{Commits}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 77 & 100\% \\
Declan Young & 23 & 29.9\% \\
Aidan Mariglia & 0 & 0.0\% \\
Nathan Uy & 52 & 67.5\% \\
Ben Dubois & 2 & 2.6\% \\
\bottomrule
\end{tabular}
\end{table}

All major commits (doc) are co-authored by all team members (like the design document). Nathan has 52 commits due to testing of CI/CD, which was not squashed upon merging. 

\section{Issue Tracker}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Declan Young & 8 & 2 \\
Aidan Mariglia & 0 & 7 \\
Nathan Uy & 7 & 2 \\
Ben Dubois & 1 & 4 \\
\bottomrule
\end{tabular}
\end{table}

Most issues were done collaboratively.

\section{CICD}

CI/CD will be used to enforce branch protection and maintain code quality, running static checks against the code base as well as requiring all existing unit tests to pass before a feature branch can be merged to the main branch.

\end{document}